\section{References}
\begin{enumerate}
\item E. Clementi and C. Roetti, in Atomic Data and Nuclear Data 
Tables, Vol. 14, pages 177-478 (1974).

\item C. Moore, in Ionization Potentials, NSRDS-NBS, Vol. 34 
(1970).

\item H. Hotop and W. C. Lineberger, in J. Phys. Chem. Ref. 
Data., Vol. 4, page 568 (1975).

\item E. Clementi and D. L. Raimondi, in J. Chem. Phys., Vol. 38, 
page 2686 (1963).
\end{enumerate}

\section{Excercises}
\begin{enumerate}
\item From Section 5.2.  Use the functions given in Table \ref{chap5-table2} to 
determine the positions of the maxima of $\phi , r \phi$, and $(r
\phi)^2$.

\item Defining ${\bar r}$ as
\begin{equation}
{\bar r} = \sqrt{\langle \psi | r^2 | \psi \rangle}
\end{equation}
find ${\bar r}$ for the radial functions in Table \ref{chap5-table2}.
\end{enumerate}


\section{Reference}
\begin{enumerate}
\item  E. U. Condon and G. H. Shortley, in Theory of Atomic 
Spectra, Cambridge University Press, pages 76 and 77 (1963).
\end{enumerate}

\section{Exercises}
\begin{enumerate}
\item From Appendix A.  Consider the case of $p^3$ and (a) derive 
the allowed symmetries.  (b) Write down the wavefunctions for each 
state, use real or complex functions, whichever suits you.  (c) Find 
the energy expression for each state, use real or complex 
wavefunctions, whichever suits you.  What is the order of the states 
and the ratio of the energy splittings?

\item Consider the case of $p^4$, show how to relate the energies 
of the states to the expressions obtained for $p^2$.

\item Consider the case of $(d)^2$ and (a) derive the allowed 
symmetries.  (b) Write down the wavefunctions for each state, use real 
or complex functions, whichever suits you.  (c) Find the energy 
expression for each state, use real or complex wavefunctions, 
whichever suits you.  What is the order of the states and the ratio of 
the energy splittings?
\end{enumerate}
