\noindent{{\bf 6.9  References}}

\item {1.} C. E. Moore, in Atomic Energy Levels, Vol. 1, circular 
467, U. S. National Bureau of Standards, Washington, D. C., Government 
Printing Office, page 309 (1949).

\item {2.} B. Rosen, in Spectroscopic Data Relative to Diatomic 
Molecules, Oxford, England, Pergamon Press, page 515 (1970).

\item {3.} K. P. Huber and G. Herzberg, in Constants in Diatomic 
Molecules, Princeton, New Jersey, D. Van Nostrand (1979).

\item {4.} S. N. Suchard, in Spectroscopic Constants for Selected 
Heteronuclear Diatomic Molecules, El Segundo, California, the 
Aerospace Corporation, page 1452 (1974).

\item {5.} G. Herzberg, in Electron Spectra and Electronic Structure 
of Polyatomic Molecules, Princeton, New Jersey, D. Van Nostrand, page 
745 (1967).

\item {6.} D. R. Stull and H. Prophet, in JANAF Thermochemical 
Tables, NSRDS-NBS 37, Washington, D. C., U. S. Government Printing 
Office, page 1141 (1971).

\item {7.} D. D. Wagman, W. H. Evans, V. B. Parker, I. Halow, S. M. 
Bailey, and R. H. Schumm, in NBS Technical Note 270-3, Washington, D. 
C., U. S. Government Printing Office, page 264 (1965).

\item {8.} A. F. Voter and W. A. Goddard III, unpublished work.

\item {9.} I. Dubois, Canadian J. of Physics, vol. 46, page 2485 
(1968).  J. W. Meadows and H. F. Schaefer III, in J. Am. Chem. Soc., 
vol. 98, page 4383 (1976).  M. M. Heaton, in J. Chem. Phys., vol. 67, 
page 5396 (1977).  B. Wirsam, in Chem. Phys. Lett., vol. 10, page 180 
(1971).

\item {10.} M. L. Steigerwald and W. A. Goddard III, unpublished work.

\item {11.} E. A. Carter and W. A. Goddard III, (1983).

\item {12.} P. J. Hay, W. J. Hunt, and W. A. Goddard III, in J. Am. 
Chem. Soc., vol. 94, page 8293 (1972).

\item {13.} F. W. Bobrowicz, in Investigations of Spin-Eigenfunction 
Correlated Wavefunctions, Ph.D. Thesis, California Institute of 
Technology (1974).

\item {14.} W. A. Goddard III and R. J. Blint, in Chem. Phys. Lett., 
vol. 14, page 616 (1972).

\item {15.} J. P. Dwyer and W. A. Goddard III, unpublished results.

\item {16.} L. B. Harding and W. A. Goddard III, in J. Chem. Phys., vol. 
67, page 1777 (1977).  A. Kasdan, E. Herbst, and W. C. Lineberger, in 
Chem. Phys. Lett., vol. 31, page 78 (1975).

\item {17.} L. B. Harding and W. A. Goddard III, in Chem. Phys. Lett., 
vol. 55, page 217 (1978).  B. O. Roos and P. M. Siegbahn, in J. Am. 
Chem. Soc., vol. 99, page 7716 (1977).  R. R. Lucchese and H. F. 
Schaefer III, in J. Am. Chem. Soc., vol. 99, page 6765 (1977).  C. W. 
Bauschlicher and I. Shavitt, in J. Am. Chem. Soc., vol. 99 (1978).

\item {18.} G. T. Surratt and W. A. Goddard III, in Chem. Phys., vol. 
23, page 39 (1977).

\item {19.} W. J. Hunt, P. J. Hay, and W. A. Goddard III, unpublished 
results.

\item {20.} C. W. Bauschlicher Jr., H. F. Schaefer III, and P. S. 
Gabus, in J. Am. Chem. Soc., vol. 99, page 7106 (1977).

\item {21.}	R. J. Buenker and S. D. Peyerimhoff, in Chem. Rev., vol. 74, 
page 127 (1974).

\item {22.}	S. P. Richards, in Int. J. Quant. Chem., vol. 11, page 
73 (1977).  A. Schmiedekamp, S. Skaarup, P. Pulay, and J. E. Boggs, 
in J. Chem. Phys., Vol. 66, page 5769 (1977).  R. Ahlrichs, F. Keil, 
H. Ischka, W. Kutzenlnigg, and V. Staemmler, in J. Chem. Phys., vol. 
63, page 455 (1977).
\vfill\eject

